---
title: "Week 9, Day 2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(PPBDS.data)
library(rstanarm)
library(tidyverse)

# There is one change to our data from Tuesday. We have a created a new
# variable: `poverty_n`, where the "n" stands for "normalized." To normalize data
# is to subtract the mean and divide by the standard deviation. This can be
# helpful. The coefficient to such a variable can be interpreted as a comparison
# between two groups, separated by a one standard deviation of the poverty
# measure.


week_9 <- kenya %>% 
  rename(reg_chg = reg_byrv13) %>% 
  filter(treatment %in% c("control", "local")) %>% 
  droplevels() %>% 
  mutate(poverty_n = (poverty - mean(poverty))/sd(poverty)) %>% 
  select(poll_station, reg_chg, treatment, poverty_n, poverty)
  
```


## Scene 1

**Prompt:** Let's create a new model. Consider `reg_chg` as a function of `treatment`, `poverty_n` and the interaction between the two.

* Write the math for this model.

$$reg\_chg_i = \beta_0 + \beta_1 local_i + \beta_2 poverty\_n_i + \\ \beta_3 local_i * poverty\_n_i + \epsilon_i $$

* Describe the population for which you are creating the model.

* Fit the  model and interpret the coefficients. Focus on the coefficient of the interaction term.

```{r}
fit_obj <- stan_glm(formula = reg_chg ~ treatment + poverty_n + treatment * poverty_n,
                    data = week_9,
                    refresh = 0)
```

```{r}
print(fit_obj, digits = 5)
```


## Scene 2

**Prompt:** Let's begin with a question from Kenyan President Uhuru Kenyatta:

*Consider the polling station 007/001. What are the chances of an increase in registration of 4% if I were to give it the local treatment in January?*

Write a sentence or two for each of these topics:

* What would Wisdom suggest about the use of the `kenya` data to answer this question?

* Describe the ideal Preceptor Table.

* Graph the posterior probability distribution `reg_chg` if polling station 007/001 were to be assigned treatment in January.

```{r}
new_obs <- tibble(treatment = "local", poverty_n = -1.61)

pp <- posterior_predict(fit_obj, newdata = new_obs) %>% 
  as_tibble()

pp %>% 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count / sum(count))),
                   bins = 100)
```


* Answer the President's question.

```{r}
pp %>% 
  filter(`1` > 0.04)
```



## Scene 3


**Prompt:**  President Kenyatta has another question:

*I care more about increasing registration in poor communities. For a community with poverty_n equal to 2, what would you expect the change in registration under treatment to be?*

Using the model which you created in Scene 1, create a graphic of the posterior probability distribution of the causal effect of `local` treatment in polling stations which have +2 sigma poverty rates. Note that there are two ways to do this. First, we can use a parameter approach. This is what we did in class last week. Second, we can use `posterior_epred()`, which is generally easier since it does the math for us. Use the `posterior_epred()` approach. 

```{r}
new_obs_2 <- tibble(treatment = "local", poverty_n = 0)

pe <- posterior_epred(fit_obj, newdata = new_obs_2) %>% 
  as_tibble()

pe %>% 
  ggplot(aes(x = `1`)) +
    geom_histogram(aes(y = after_stat(count / sum(count))),
                   bins = 100)
```


